Social Feedback For Robotic Collaboration

### 2016-05-22 paper.tex
removed thesis, fixed punctuation, spelling

Feedback refers to the responses that are received by an agent when it takes some action. These feedback responses inform the agent about the success or failure of its actions. \emph{Social feedback} therefore refers to social signals that convey this information. These can be explicit signals, such as ``I want this object'', or implicit signals, such as a perplexed expression. When humans interact with another human, they use this feedback to improve the flow and clarity of the collaboration, which in turn improves its success. For my thesis work, I have developed a framework that describes how robotic agent should likewise generate social feedback for its human partner in human-collaborative tasks, and show that it improves the speed and accuracy of human-robot interaction.

Many existing works focus on the task of interpreting human communications\citep{tellex11,matuszek12,tellex12,misra14}, but provide no response if the interpretation fails. As a consequence, it becomes difficult to tell whether the robot is still making progress in interpreting the request, or has failed. Some works do allow for robotic responses to ambiguous situations, but the manner of their responses are hard coded, often limited to generic requests, such as ``please repeat the question''. In this work, we provide a means to generate these requests in the form of language and gesture that can flexibly represent the robot's state as well as inform the human in such a way so that allows the human to help the robot as much as possible.

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[scale=0.17]{resources/firstPerson}
		\caption{The experimental setup from the participant's perspective: a Baxter robot has six objects within reach. The participant stands in front of the table to provide speech and gesture requests}
	\end{center}
\end{figure}

@@

Alternative approaches to
POMDPs include cognitive architecutres such as SOAR~\citep{soar} or
DIARC~\citep{diarc}.  By taking a probabilistic approach, we can seemlessly
fuse information from multiple sources and explicitly reason about the
robot's uncertainty when choosing actions.
\section{Technical Approach}

@@

	\item $T(s, a, s^\prime) = p(s^\prime | s, a)$. We make the assumption that the human's desired object $\iota$ does not change unless the robot picks up object $\iota$. The set of all objects $\Iota$ transistions to $\Iota \setminus \{i\}$ when the robot chooses action \texttt{pick(i)}. For each action in $A$, we define a ``reverse observation function'' that describes our assumptions about how the human imagines the robot generates actions (which the human sees as observations) given a hidden robot state. This allows us to define a transition function for $\beta$. The transition dynamics are described in greater detail in section  \ref{sssec:tf}. 

@@

	\item Observation $o \in \Omega$ represents an observation generated by the human. These are tuples of language and gesture: $\langle l, g \rangle$. Language utterance $l$ is represented by a string of any number of words, obtained by transcribing microphone input using webkit's speech recognition API through google chrome.  A gesture $g$ is represented by a vector from the participant's shoulder to their wrist, and all gestures are interpreted as a straight-armed point. This vector is obtained using the Kinect's tracking software. 

@@

To account for suboptimal behavior and avoid irregularities in our observation function, we soften our assumptions of optimality such that $1-\epsilon$ fraction of the time, the human chooses the optimal action. With probability $\epsilon$ they pick acccording to the base-level observation function described above.

@@

First, we will define a toy domain. In this toy domain, the states are the following: $\{AA, AB, BA, BB\}$ as well as $\beta$, which is a distribution over these states. The observations are $\{A\_, \_A, B\_, \_B\}$, which mean ``the first character is an A'', ``the second character is an A'', ``the first character is B'', ``and the second character is a B'' respectively. These observations are provided by the human. The agent can take actions $CX$ which is informing the human that the agent believes the Xth character is a C, as well as ``picking'' the object or waiting. For the basel level observation, the human always gives truthful observations, and has equal probability of generating an observation pertaining to a particular character. We will see how this affects the POMDP observation function, which incorporates $\beta$.

@@

Intially both $b$, the robot's belief about the human's desired object and $\beta$, the human's belief about the robot's belief, are uniform. The true state is $AA$.

@@

\begin{figure}[H]
\begin{center}
	\includegraphics[width=0.45\textwidth]{resources/results}
\end{center}
\caption{Results in simulation. \texttt{turns\_until\_pick} is the number of timesteps until first correct pick,  \texttt{pick\_acc} is the ratio of correct picks to total picks, \texttt{avg\_time} is the the time to compute a single action}
	\label{fig:toyresults}
\end{figure}

@@

This thesis work relies on very simple observation functions. In the future, we will investigate more sophisticated observation functions, allowing for language interpretation that can understand prepositional phrases and other ways of composing referring expressions.

@@

>>>>

Feedback refers to the responses that are received by an agent when it takes some action. These feedback responses inform the agent about the success or failure of its actions. \emph{Social feedback} therefore refers to social signals that convey this information. These can be explicit signals, such as ``I want this object,'' or implicit signals, such as a perplexed expression. When humans interact with another human, they use this feedback to improve the flow and clarity of the collaboration, which in turn improves its success. In this paper, we describe a  framework that describes how robotic agent should likewise generate social feedback for its human partner in human-collaborative tasks, and show that it improves the speed and accuracy of human-robot interaction.

Many existing works focus on the task of interpreting human communications\citep{tellex11,matuszek12,tellex12,misra14}, but provide no response if the interpretation fails. As a consequence, it becomes difficult to tell whether the robot is still making progress in interpreting the request, or has failed. Some works do allow for robotic responses to ambiguous situations, but the manner of their responses are hard coded, often limited to generic requests, such as ``please repeat the question.'' In this work, we provide a means to generate these requests in the form of language and gesture that can flexibly represent the robot's state as well as inform the human in such a way so that allows the human to help the robot as much as possible.

@@

\begin{figure}[t]
	\begin{center}
		\includegraphics[scale=0.17]{resources/firstPerson}
		\caption{The experimental setup from the participant's perspective: a Baxter robot has six objects within reach. The participant stands in front of the table to provide speech and gesture requests}
	\end{center}
\end{figure}

@@

Alternative approaches to
POMDPs include cognitive architectures such as SOAR~\citep{soar} or
DIARC~\citep{diarc}.  By taking a probabilistic approach, we can seamlessly
fuse information from multiple sources and explicitly reason about the
robot's uncertainty when choosing actions.
\section{Technical Approach}

@@

	\item $T(s, a, s^\prime) = p(s^\prime | s, a)$. We make the assumption that the human's desired object $\iota$ does not change unless the robot picks up object $\iota$. The set of all objects $\Iota$ transitions to $\Iota \setminus \{i\}$ when the robot chooses action \texttt{pick(i)}. For each action in $A$, we define a ``reverse observation function'' that describes our assumptions about how the human imagines the robot generates actions (which the human sees as observations) given a hidden robot state. This allows us to define a transition function for $\beta$. The transition dynamics are described in greater detail in section  \ref{sssec:tf}. 

@@

	\item Observation $o \in \Omega$ represents an observation generated by the human. These are tuples of language and gesture: $\langle l, g \rangle$. Language utterance $l$ is represented by a string of any number of words, obtained by transcribing microphone input using webkit's speech recognition API through Google Chrome.  A gesture $g$ is represented by a vector from the participant's shoulder to their wrist, and all gestures are interpreted as a straight-armed point. This vector is obtained using the Kinect's tracking software. 

@@

To account for suboptimal behavior and avoid irregularities in our observation function, we soften our assumptions of optimality such that $1-\epsilon$ fraction of the time, the human chooses the optimal action. With probability $\epsilon$ they pick according to the base-level observation function described above.

@@

First, we will define a toy domain. In this toy domain, the states are the following: $\{AA, AB, BA, BB\}$ as well as $\beta$, which is a distribution over these states. The observations are $\{A\_, \_A, B\_, \_B\}$, which mean ``the first character is an A'', ``the second character is an A'', ``the first character is B'', ``and the second character is a B'' respectively. These observations are provided by the human. The agent can take actions $CX$ which is informing the human that the agent believes the Xth character is a C, as well as ``picking'' the object or waiting. For the base level observation, the human always gives truthful observations, and has equal probability of generating an observation pertaining to a particular character. We will see how this affects the POMDP observation function, which incorporates $\beta$.

@@

Initially both $b$, the robot's belief about the human's desired object and $\beta$, the human's belief about the robot's belief, are uniform. The true state is $AA$.

@@

\begin{figure}[H]
\begin{center}
	\includegraphics[width=0.45\textwidth]{resources/results}
\end{center}
\caption{Results in simulation. \texttt{turns\_until\_pick} is the number of timesteps until first correct pick,  \texttt{pick\_acc} is the ratio of correct picks to total picks, \texttt{avg\_time} is the time to compute a single action}
	\label{fig:toyresults}
\end{figure}

@@

In the future, we will investigate more sophisticated observation functions, allowing for language interpretation that can understand prepositional phrases and other ways of composing referring expressions.

@@

\exwnote{I may remove this section, unless there is more to add}
